DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-14 ase2017/paper.tex
Added connections to ASE topics
Added brief mention of future work relevant to ASE community.

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB either as a
transfer function or a state-space equation.  The \tool is the first fully
automated synthesis tool that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant
dynamics~\cite{abate2017, abatecav2017}.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants that considers all aspects of their digital
implementation.
%
As future work, the \tool will perform synthesis considering additional
requirements (e.g., performance) and will be combined with the
DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
verify/validate further controller properties.

>>>>

The \tool can automatically synthesize stable and safe digital controllers
for intricate dynamic physical plants, represented in MATLAB either as a
transfer function or a state-space equation.  The \tool is the first fully
automated synthesis tool that is algorithmically and numerically sound,
considering various error sources in the implementation of the digital
control algorithm and in the computational modeling of plant
dynamics~\cite{abate2017, abatecav2017}.
%
The \tool presents a practical application of CEGIS-based program synthesis.
Tractable program synthesis in control engineering encourages the application
of this technique in other fields such as program repair or superoptimisation.
Future work of this group will pursue the application of CEGIS to software
engineering problems.
%
Additionally, given the current literature in controller synthesis, there is
no other MATLAB toolbox for synthesizing stable and safe digital controllers
for physical plants that considers all aspects of their digital
implementation.
%
As future work, the \tool will perform synthesis considering additional
requirements (e.g., performance) and will be combined with the
DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to
verify/validate further controller properties.
